---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {wontrun}

<!-- badges: start -->
<!-- badges: end -->

The goal of retrex is to make it easy to run examples from archived package source on current versions of packages in order
to test RETRocompatibility of EXamples and ultimately evaluate reproducibility of code.

## Installation

`{retrex}` is not available on CRAN, but you can install the development version of retrex like so:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("b-rodrigues/wontrun", ref = "master")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wontrun)

```

```{r}
aer_sources <- get_archived_sources("AER")

```

```{r}
aer_sources

```

```{r, echo = F}
aer_runs <- aer_sources %>%
  wontrun(ncpus = 6, years = 2008)
```


```{r}
summary_wontrun(aer_runs)
```
