---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {wontrun}

<!-- badges: start -->
<!-- badges: end -->

The goal of {wontrun} is to test the longevity of old code for the R programming language by making
it easy to run examples from archived package sources on current versions of packages.

## Installation

`{retrex}` is not available on CRAN, but you can install the development version of retrex like so:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("b-rodrigues/wontrun", ref = "master")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wontrun)

```

```{r}
aer_sources <- get_archived_sources("AER")

```

```{r}
aer_sources

```

```{r, eval = F}
aer_runs <- aer_sources %>%
  wontrun(ncpus = 6, years = 2008)
```

```{r, include = F}
aer_runs <- aer_sources %>%
  wontrun(ncpus = 6, years = 2008)
```

```{r}
summary_wontrun(aer_runs)
```

## Thanks

- Thanks to [Dirk Eddelbuettel](https://twitter.com/eddelbuettel/status/1588149491772923907?s=20&t=aRcs1VTwn1861biBikjdiA) for the idea!
- Thanks to [Deemah](https://fediscience.org/@dmi3kno/109296599193965025) for suggesting the name of the package!
- Thanks to [Jenny Bryan](https://twitter.com/JennyBryan/status/1590788394405498880?s=20&t=aRcs1VTwn1861biBikjdiA) for suggesting using `{callr}` which I use in this package.
- Thanks to [David Hood](https://mastodon.nz/@thoughtfulnz/109330296529120658) for suggesting the term *code longevity*.
- and thanks to [everyone on Mastodon](https://fosstodon.org/@brodriguesco/109330164860035432) for the helpful discussions!
