---
title: "Running old examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{running_old_examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(wontrun)
library(dplyr)
library(purrr)
```

We need to start with a list of packages. Two functions can be used for this, either 
`get_archived_sources()`, which takes a package name, or `get_packages_from_view()`,
which takes the name of a CRAN Task View, and optionally a date.

Get the archived sources for the `{dplyr}` package:

```{r}
dplyr_sources <- get_archived_sources("dplyr")
```

This is what it looks like:

```{r}
dplyr_sources
```

Let's also choose how many cores we want to use to run the examples, as this is a 
time-consuming operation:

```{r, eval = F}
cl <- parallel::detectCores()-2
```

We can now run the examples contained in the archived packages with the `wontrun()` function:

```{r, eval = F}
dplyr_runs <- wontrun(dplyr_sources, ncpus = cl)
```

```{r, echo = f}
dplyr_runs <- readRDS("dplyr_runs.Rds")
```


Using `get_packages_from_view()`, we get a 
data frame with packages from a CRAN Task View. But you can provide any data frame
with a column called `name` where each element is a package name. The lines below 
show you how to get a data frame, called `econ_source` that contains the packages
from the `Econometrics` view as of "2015-01-01". 

```{r, eval = F}
ctv_econ <- get_packages_from_view("Econometrics", date = "2015-01-01")
econ_source <- get_sources_for_selected_packages(ctv_econ)
```

To make things easier, you can load a sample of packages with the following
line:

```{r}
data("sources_ctv_econ")

sources_ctv_econ
```

It is now possible to download the documentation from the packages to a temporary directory
with:

```{r}
sources_ctv_econ_with_path <- get_examples(sources_ctv_econ)
```

```{r}
hu <- run_examples(filter(sources_ctv_econ_with_path, name == "gmm"))
```
